---
title: "Class4"
author: "Maris Sala"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#just coding loops
parameter recovery - still
```{r}
set.seed(1982)
setwd("~/Aarhus University/Advanced cog mod/progre")
library(R2jags)
```


Recover dif parameter combinations for the learning model
```{r}
#the alpha we put in
trueAlpha <- array(0,c(20))
inferredAlpha <- array(c(20)) #map

trueTheta <- array(0,c(20))
inferredTheta <- array(c(20))

ntrials <- 100

for (i in 1:20) {
  Glearn <- array(0, c(100)) #guess for our learning model
  theta <- array(0, c(100)) #theta is going to update every trial
  # we need a starting theta!
  alpha <- runif(1,0,1)#learning rate, 
  theta1 <- runif(1,0,1)
  
  #need a theta on trial 1, have to define the 1st trial, simulation runs from trial 2
  theta[1] <- theta1
  Glearn[1] <- rbinom(1,1,theta[1])
  
  for (t in 2:ntrials) {
    
    theta[t] <- theta[t-1]^(1/(1+alpha)) #this is the learning rule/curve, focus on this next week
    Glearn[t] <- rbinom(1,1,theta[t])
  
  }
  
  trueAlpha[i] <- alpha
  trueTheta[i] <- theta1
  
  # ---- run inference for the learning model using learning simulations
  G <- Glearn

  data <- list("G", "ntrials") #has to be a list in this case, look in the workspace for G
  params <- c("theta", "theta1", "alpha") #what are we interested in keeping track of, theta as a distribution
  
  samples <- jags(data, inits = NULL, params,
                  model.file = "chick_learning.txt",
                  n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1)
  
  alpha.post <- samples$BUGSoutput$sims.list$alpha
  #max a posteriori for alpha
  inferredAlpha[i] <- density(alpha.post)$x[which(density(alpha.post)$y==max(density(alpha.post)$y) )]
  
  theta1.post <- samples$BUGSoutput$sims.list$theta1
  #max a posteriori for alpha
  inferredTheta[i] <- density(theta1.post)$x[which(density(theta1.post)$y==max(density(theta1.post)$y) )]
}


```

```{r}
plot(trueAlpha,inferredAlpha)
plot(trueTheta, inferredTheta)
```

Model recovery!
have to have 1 model thats better than the other bc we are using the DIC to compare 2 models
use the fixed model and learning model as a control against each other

```{r}

#model comparison - homework

## MODEL 1: Fixed Theta model ##
Gfixed <- array(0, c(100)) #100 elements of 0s
#array(0, c(2,100)) if theres 2 agents for example
#empty array we will fill up with a simple forward model

#need a fixed parameter
theta <- .7 #anything thats less than 0 more than 1 is not legit
#someone who is okay at this task

ntrials <- 100

for (t in 1:ntrials) {
  Gfixed[t] <- rbinom(1,1,theta) #each element in the array populated with consequences of the model
}

# MODEL 2
Glearn <- array(0, c(100)) #guess for our learning model
theta <- array(0, c(100)) #theta is going to update every trial
# we need a starting theta!
alpha <- .05 #learning rate, can never be interpreted contextually free
theta1 <- .5

ntrials <- 100

#need a theta on trial 1, have to define the 1st trial, simulation runs from trial 2
theta[1] <- theta1
Glearn[1] <- rbinom(1,1,theta[1])

for (t in 2:ntrials) {
  
  theta[t] <- theta[t-1]^(1/(1+alpha)) #this is the learning rule/curve, focus on this next week
  Glearn[t] <- rbinom(1,1,theta[t])

}


# -- run inference for fixed data and fixed model
G <- Gfixed

data <- list("G", "ntrials") #has to be a list in this case, look in the workspace for G
params <- c("theta") #what are we interested in keeping track of, theta as a distribution

samples <- jags(data, inits = NULL, params,
                model.file = "chick.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1) #inits could be important when there are convergence issues

DIC.fixed_fixed <- samples$BUGSoutput$DIC

# put fixed data in the learning model
G <- Glearn

data <- list("G", "ntrials") #has to be a list in this case, look in the workspace for G
params <- c("theta") #what are we interested in keeping track of, theta as a distribution

samples <- jags(data, inits = NULL, params,
                model.file = "chick.txt", #DONT CHANGE THE FILE HERE!
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1) #inits could be important when there are convergence issues

DIC.learning_fixed <- samples$BUGSoutput$DIC

# fixed data to learning model
G <- Gfixed

data <- list("G", "ntrials") #has to be a list in this case, look in the workspace for G
params <- c("theta") #what are we interested in keeping track of, theta as a distribution

samples <- jags(data, inits = NULL, params,
                model.file = "chick_learning.txt", #DONT CHANGE THE FILE HERE!
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1) #inits could be important when there are convergence issues

DIC.fixed_learning <- samples$BUGSoutput$DIC


# fixed data to learning model
G <- Glearn

data <- list("G", "ntrials") #has to be a list in this case, look in the workspace for G
params <- c("theta") #what are we interested in keeping track of, theta as a distribution

samples <- jags(data, inits = NULL, params,
                model.file = "chick_learning.txt", #DONT CHANGE THE FILE HERE!
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1) #inits could be important when there are convergence issues

DIC.learning_learning <- samples$BUGSoutput$DIC


DIC.fixed_fixed
DIC.learning_fixed
DIC.fixed_learning
DIC.learning_learning

```
DIC fixed should be lower than DIC learning because its its own model - so this is crap model recovery
make a confusion matrix!