---
title: "Class14"
author: "Maris Sala"
date: "4/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hierarchical models of PVL, ORL and VSE

Setup
```{r}
set.seed(1982)
#setwd("~/Aarhus University/Advanced cog mod/progre")
pacman::p_load(extraDistr, R2jags)

# load control data
ctr_data <- read.table("rawData/IGTdata_healthy_control.txt", header=T)
```

Prepare the data for the JAGS model
Turning it into a matrix
```{r}
# Identify and count unique subject IDs
subIDs <- unique(ctr_data$subjID)
nsubs <- length(subIDs)
ntrials_max <- 100

# All choices (x) and outcomes (X)
x_raw <- ctr_data$deck
X_raw <- ctr_data$gain + ctr_data$loss
```

Assign choices and outcomes in trial x sub matrix
Different number of trials across subjects. We'll need to fix this by padding arrays of < 100. Then we'll also need to record number of valid trials for each sub, then run the JAGS model on only valid trials!
```{r}
# Empty arrays to fill
ntrials_all <- array(0, c(nsubs))
x_all <- array(0, c(nsubs, ntrials_max))
X_all <- array(0, c(nsubs, ntrials_max))

# Fill the arrays! Loop over subjects
for (s in 1:nsubs) {
  
  #record n trials for subject s. Count number of trials for subject
  ntrials_all[s] <- length(x_raw[ctr_data$subjID==subIDs[s]])
  
  #pad trials with NA if n trials < maximum (i e 100)
  x_sub <- x_raw[ctr_data$subjID==subIDs[s]]
  length(x_sub) <- ntrials_max
  
  X_sub <- X_raw[ctr_data$subjID==subIDs[s]]
  length(X_sub) <- ntrials_max
  #^temporary data for subject s, padded with NA where there are no trials, the NA's do NOT get into JAGS!
  
  #assign arrays
  x_all[s,] <- x_sub
  X_all[s,] <- X_sub
}
```

RUNNING THE HIERARCHICAL PVL MODEL
```{r}
#ohlawd
x <- x_all
X <- X_all

#set up jags and run it
data <- list("x", "X", "ntrials_all", "nsubs")
params <- c("mu_w","mu_A","mu_theta","mu_a","lambda_w","lambda_A","lambda_theta","lambda_a")

samples <- jags.parallel(data, inits = NULL, params,
                model.file = "jags_models/hPVL.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1);beepr::beep(sound=9)

par(mfrow=c(2,2))
plot(density(samples$BUGSoutput$sims.list$mu_w))
plot(density(samples$BUGSoutput$sims.list$mu_A))
plot(density(samples$BUGSoutput$sims.list$mu_theta))
plot(density(samples$BUGSoutput$sims.list$mu_a))
plot(density(samples$BUGSoutput$sims.list$lambda_w))
plot(density(samples$BUGSoutput$sims.list$lambda_A))
plot(density(samples$BUGSoutput$sims.list$lambda_theta))
plot(density(samples$BUGSoutput$sims.list$lambda_a))

```


Trying out saving the samples
```{r}
save.image(file='hPVL_model_samples.RData')
load("hPVL_model_samples.RData")
```


Hierarchical ORL
```{r}
#ohlawd
x_ctr <- x_all
# Divide by 100
X_ctr <- X_all/100

ntrials_ctr <- ntrials_all
nsubs_ctr <- nsubs

## RUN THIS AGAIN WITH THE CORRECT LAMBDAS PLUS CORRECT PAYOFF
#set up jags and run it
data <- list("x_ctr", "X_ctr", "ntrials_ctr", "nsubs_ctr")
params <- c("mu_a_rew","mu_a_pun","mu_K","mu_omega_f", "mu_omega_p",
            "lambda_a_rew_ctr","lambda_a_pun_ctr","lambda_K_ctr","lambda_omega_f_ctr", "lambda_omega_p_ctr")

samples2 <- jags.parallel(data, inits = NULL, params,
                model.file = "jags_models/hORL.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1);beepr::beep(sound=3)

par(mfrow=c(3,2))
plot(density(samples2$BUGSoutput$sims.list$mu_a_rew))
plot(density(samples2$BUGSoutput$sims.list$mu_a_pun))
plot(density(samples2$BUGSoutput$sims.list$mu_K))
plot(density(samples2$BUGSoutput$sims.list$mu_omega_f))
plot(density(samples2$BUGSoutput$sims.list$mu_omega_p))
par(mfrow=c(3,2))
plot(density(samples2$BUGSoutput$sims.list$lambda_a_rew_ctr))
plot(density(samples2$BUGSoutput$sims.list$lambda_a_pun_ctr))
plot(density(samples2$BUGSoutput$sims.list$lambda_K_ctr))
plot(density(samples2$BUGSoutput$sims.list$lambda_omega_f_ctr))
plot(density(samples2$BUGSoutput$sims.list$lambda_omega_p_ctr))
```


Save samples
```{r}
save.image(file='hORL_model_samples.RData')
load("hPVL_hORL_hVSE_model_samples.RData")
```


Hierarchical VSE
```{r}
# Data prep
X_raw <- ctr_data$gain
Y_raw <- ctr_data$loss

ntrials_all <- array(0,c(nsubs)) #how many trials each sub made it through
x_all <- array(0,c(nsubs,ntrials_max))
X_all <- array(0,c(nsubs,ntrials_max)) #our two target arrays for this model (one for x and one for X)
Y_all <- array(0,c(nsubs,ntrials_max))

for (s in 1:nsubs) {
  #record n trials for subject s
  ntrials_all[s] <- length(x_raw[ctr_data$subjID==subIDs[s]])
  
  #pad trials with NA if n trials < maximum (i.e. 100)
  x_sub <- x_raw[ctr_data$subjID==subIDs[s]]
  length(x_sub) <- ntrials_max
  
  X_sub <- X_raw[ctr_data$subjID==subIDs[s]]
  length(X_sub) <- ntrials_max
  
  Y_sub <- Y_raw[ctr_data$subjID==subIDs[s]]
  length(Y_sub) <- ntrials_max
  
  #assign arrays
  x_all[s,] <- x_sub
  X_all[s,] <- X_sub
  Y_all[s,] <- Y_sub
  
}

x <- x_all
X <- X_all
Y <- Y_all

Y <- abs(Y)

#set up jags and run jags model

data <- list("x","X","Y", "ntrials_all", "nsubs")
params <- c("mu_alpha", "mu_theta", "mu_delta", "mu_phi", "mu_beta", "lambda_alpha", "lambda_theta", "lambda_delta", "lambda_phi", "lambda_beta")

samples3 <- jags.parallel(data, inits = NULL, params,
                model.file = "jags_models/hVSE.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1);beepr::beep(sound=9)


#posterior distribution plots:
par(mfrow=c(3,2))
plot(density(samples3$BUGSoutput$sims.list$mu_alpha))
plot(density(samples3$BUGSoutput$sims.list$mu_theta))
plot(density(samples3$BUGSoutput$sims.list$mu_delta))
plot(density(samples3$BUGSoutput$sims.list$mu_phi))
plot(density(samples3$BUGSoutput$sims.list$mu_beta))
par(mfrow=c(3,2))
plot(density(samples3$BUGSoutput$sims.list$lambda_alpha))
plot(density(samples3$BUGSoutput$sims.list$lambda_theta))
plot(density(samples3$BUGSoutput$sims.list$lambda_delta))
plot(density(samples3$BUGSoutput$sims.list$lambda_phi))
plot(density(samples3$BUGSoutput$sims.list$lambda_beta))

```

Save samples
```{r}
save.image(file='hPVL_hORL_hVSE_model_samples.RData')
load("hPVL_hORL_hVSE__model_samples.RData")
```
